Notes

### 2024-05-30 notes.qmd
update

-   Analysis
    -   [ ] Contribution of discontinuities to the power spectrum
    -   [ ] Check Datagap
    -   [ ] Check `ARTEMIS-B` data in different states (solar wind, magnetosheath, magnetotail, moon wake)
    -   [ ] Distribution of \|B\| over radius
    -   [ ] JUNO from 2012-09\~2012-10 lack of IDS and extreme large thickness
    -   [ ] Wind data
    -   [ ] Add error bar
    -   [ ] Validate the effects of calibrate candidate duration
    -   [ ] Validate model density with `Voyager`
-   Identifaction
    -   [ ] Ensemble forest?
    -   [ ] Smoothing is important?
    -   [ ] Check change point algorithm
-   Visualize data gaps
-   Features
    -   [ ] Thickness in N direction
    -   [ ] Use high resolution data for feature extraction
-   Compare with other methods of identifying IDs
    -   [ ] Verify with other methods of identifying IDs
-   [x] Incorporate solar wind propagation model
    -   [x] Verify with solar wind propagation model
        -   [x] Coordinate transformation

>>>>

-   Analysis
    -   [ ] Re-calculate the occurrence rate of IDs
    -   [ ] Contribution of discontinuities to the power spectrum
    -   [ ] Check Datagap
    -   [ ] Check `ARTEMIS-B` data in different states (solar wind, magnetosheath, magnetotail, moon wake)
    -   [ ] Distribution of \|B\| over radius
    -   [ ] JUNO from 2012-09\~2012-10 lack of IDS and extreme large thickness
    -   [ ] Wind data
    -   [ ] Add error bar
    -   [ ] Validate the effects of calibrate candidate duration
    -   [ ] Validate model density with `Voyager`
-   Identifaction
    -   [ ] Ensemble forest?
    -   [ ] Smoothing is important?
    -   [ ] Check change point algorithm
-   Visualize data gaps
-   Features
    -   [ ] Thickness in N direction
    -   [ ] Use high resolution data for feature extraction
-   Compare with other methods of identifying IDs
    -   [ ] Verify with other methods of identifying IDs
-   [x] Incorporate solar wind propagation model
    -   [x] Verify with solar wind propagation model
        -   [x] Coordinate transformation
